### 2009-04-02 talk/icooolps2009-dotnet/benchmarks.tex
start of the icooolps .NET paper. For now, I just wrote the abstract and blindly copied the last sections from the old ecoop paper

Moreover, for each benchmark we also show the time taken by running the
equivalent program written in C\#\footnote{The sources for both TLC and C\#
  programs are available at:
  http://codespeak.net/svn/pypy/extradoc/talk/ecoop2009/benchmarks/}

The benchmarks have been run on machine with an Intel Pentium 4 CPU running at
3.20 GHz and 2 GB of RAM, running Microsoft Windows XP and Microsoft .NET
Framework 2.0.

@@

To measure how the JIT handles object-oriented features, we wrote a very
simple benchmark that involves attribute lookups and polymorphic method calls.
Since the TLC assembler source is long and hard to read,
Figure~\ref{fig:accumulator} shows the equivalent program written in an
invented Python-like syntax.

@@

As already discussed, our generated JIT does not compile the whole function at
once. Instead, it compiles and executes code chunk by chunk, waiting until it
knows enough informations to generate highly efficient code.  In particualr,
at the time it emits the code for the inner loop it exactly knows the
type of \lstinline{obj}, thus it can remove the overhead of dynamic dispatch
and inline the method call.  Moreover, since \lstinline{obj} never escapes the
function, it is \emph{virtualized} and its field \lstinline{value} is stored
as a local variable.  As a result, the generated code turns out to be a simple loop
doing additions in-place.

>>>>

Moreover, for each benchmark we also show the time taken by running the
equivalent program written in C\#.\footnote{The sources for both TLC and C\#
  programs are available at:

  http://codespeak.net/svn/pypy/extradoc/talk/ecoop2009/benchmarks/}

The benchmarks have been run on a machine with an Intel Pentium 4 CPU running at
3.20 GHz and 2 GB of RAM, running Microsoft Windows XP and Microsoft .NET
Framework 2.0.

@@

To measure how the JIT handles object-oriented features, we wrote a very
simple benchmark that involves attribute lookups and polymorphic method calls.
Since the TLC assembler source is long and hard to read,
figure~\ref{fig:accumulator} shows the equivalent program written in an
invented Python-like syntax.

@@

As already discussed, our generated JIT does not compile the whole function at
once. Instead, it compiles and executes code chunk by chunk, waiting until it
knows enough informations to generate highly efficient code.  In particular,
at the time it emits the code for the inner loop it exactly knows the
type of \lstinline{obj}, thus it can remove the overhead of dynamic dispatch
and inline the method call.  Moreover, since \lstinline{obj} never escapes the
function, it is \emph{virtualized} and its field \lstinline{value} is stored
as a local variable.  As a result, the generated code turns out to be a simple loop
doing additions in-place.
